Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Fix typo

Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatoloy (MM)
was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
sum of positive HotSpot SST Anomaly values for a pixel. **\[TI: Could you confirm the above
is described correctly?\]**

>>>>

Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatology (MM)
was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
sum of positive HotSpot SST Anomaly values for a pixel. **\[TI: Could you confirm the above
is described correctly?\]**
